Toward Centrally Programming Distributed Control Planes

### 2016-01-24 paper/evaluation.tex
adding preliminary graph for dc
added preliminary config compression results for dc
checking in changes

We have written a prototype compiler for \sysname that is implemented in roughly 5000 lines of F\# code. The compiler includes command-line flags for enabling or disabling the use of BGP MED, AS path prepending, the commonly used no-export community, as well as for ensuring k-failure safety for user-sepcified aggregates. The compiler uses regular expressions derivatives~\ref{bib:todo} with character classes to construct automata for large alphabets efficiently. The compiler uses the algorithm for computing graph dominators described in~\ref{bib:todo}. When computing local preferences and failure safety, as described in Section~\ref{sec:compilation}, the compiler performs memoization of the ``can prefer'' relation. \todo{this needs work}

@@

>>>>

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/compilation-times-dc.png}
\label{fig:compilation-times-dc}
\caption{Data center compilation times.}
\end{figure}

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/config-compression-dc.png}
\label{fig:compilation-compression-dc}
\caption{Data center config minimization.}
\end{figure}

### 2016-01-24 paper/implementation.tex
starting implementation section
checking in changes

\section{Evaluation}

We have written a prototype compiler for \sysname that is implemented in roughly 5000 lines of F\# code. The compiler includes command-line flags for enabling or disabling the use of BGP MED, AS path prepending, the commonly used no-export community, as well as for ensuring k-failure safety for user-sepcified aggregates. The compiler uses regular expressions derivatives~\ref{bib:todo} with character classes to construct automata for large alphabets efficiently. The compiler uses the algorithm for computing graph dominators described in~\ref{bib:todo}. When computing local preferences and failure safety, as described in Section~\ref{sec:compilation}, the compiler performs memoization of the ``can prefer'' relation. \todo{this needs work}

>>>>

\section{Implementation}

We have written a prototype compiler for \sysname that is implemented in roughly 5500 lines of F\# code. The compiler includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, the commonly used no-export community, as well as for ensuring at least k-failure safety for user-sepcified aggregates. Users see only ever see the high-level constraint-based language presented in Section~\ref{sec:motivation}.

\para{PG construction}

Constructing automata for extended regular expressions (regular expressions including negation and intersection) are known to have high complexity~\ref{bib:todo}. Our \sysname compiler uses regular expressions derivatives~\ref{bib:todo} with character classes to construct deterministic automata for extended regular expressions over large alphabets efficiently. Since regular expressions are defined over a finite alphabet, and since much of the AS topology is unknown, we set the alphabet to include all uniquely referenced external ASes in the policy. Similarly, to model the unknown external AS topology beyond immediate peers, we include a special topology node to represent any unknown location.

Rather than construct the product graph in full, our implementation prevents exploring parts of the graph when no accepting state is reachable in any of the corresponding regular automata during construction.

\para{PG Minimization}

Our compiler uses a fast algorithm for computing graph dominators by storing sets of dominators in a compact representation known as a dominator tree~\ref{bib:todo}.

When computing local preferences and failure safety, as described in Section~\ref{sec:compilation}, the compiler performs memoization of the ``can prefer'' relation. \todo{this needs work}

### 2016-01-24 paper/theory.tex
checking in changes

In this section we investigate the correctness and expressiveness properties of \sysname. We are mainly concerned with the following questions: (1) does the distributed, compiled policy faithfully implement the user's policy regardless of failures? (2) Are the resulting BGP configurations stable?, and (3) what polcies are or are not expressible in \sysname?

\subsection{Expressiveness}

Models for BGP are traditionally given over per-device ranked paths 
In this section, we describe the expressiveness of \sysname.

\begin{defn}

\end{defn}

@@

\begin{defn}
A distributed BGP configuration is \textit{Sound} with respect to a \sysname policy, if the only routes that that traffic ever takes in the network, are those that are specified in the policy.
\end{defn}

The Soundness claim follows directly from compilation of the product graph. Since every path through the product graph (from start to end) must match the user's policy, and since the compiled configurations use communities to ensure only valid routes through the product graph are used, the resulting BGP configurations will be Sound.

\begin{defn}
A distributed BGP configuration is \textit{Complete} with respect to a \sysname policy, if the distributed implementation always obtains a most preferred route between two nodes if the corresponding path exists in the network.
\end{defn}

The argument for completeness is as follows: Assume the most preferred path that exists in the network is between two nodes $X$ and $Y$.  This means there is a valid path in the product graph corresponding to this path, and which is available in the network. 
Assume we are unable to achieve this route in the network. To not achieve this path means that some router along advertisement route from $Y$ to $X$ preferred to accept an advertisement from another peer instead. This implies that that router that makes the ``wrong'' choice appears as a separate node in the product graph. However, from our failure safety check, we know that the other, more-preferred node must have a superset of the paths to accepting states as the less preferred node has for at least as good of a final preference. However, this implies that a route advertisement will still reach $X$, resulting in a path with a preference between $X$ and $Y$ that is just as good.

The combination of Soundness and Completeness ensures that the distributed implementation will always achieve the best routes possible, yet will never also achieve unwanted routes.

>>>>

In this section we investigate the correctness and expressiveness properties of \sysname. We are mainly concerned with answering the following questions: (1) does the distributed, compiled policy faithfully implement the user's policy regardless of failures? (2) Are the resulting BGP configurations stable?, and (3) what polcies are or are not expressible in \sysname?

%\subsection{Expressiveness}
%
%Models for BGP are traditionally given as per-device ranked paths where the configuration of each device is known ahead of time. For example router $r_1$ might have a first preference of $r_1 \cdot r_2 \cdot d$ and a second preference of $r_1 \cdot d$. Similarly, $r_2$ might have a first preference of $r_2 \cdot d$, and no other preference. Against this model of BGP we have the following.
%
%\begin{defn}
%Any policy expressible in BGP is expressible in \sysname.
%\end{defn}
%
%The proof of this is straightforward. Simply take the union of each router's rank 1 path, and make that the new most-prefered route in \sysname, and so on. For example, the above preferences would be encoded as:
%$$(r_1 \cdot r_2 \cdot d) \cup (r_2 \cdot d) \gg (r_1 \cdot d) $$
%Since the semantics of \sysname is such that each unique starting-ending locations should get their most-preferred path.

%\todo{I'm not sure if this is true}.

@@

\begin{defn}
A distributed BGP configuration is \textit{Sound} with respect to a \sysname policy, if the any route traffic takes in the network, is a valid route specified in the policy.
\end{defn}

The Soundness claim follows directly from compilation of the product graph. Since every path through the product graph (from start to end) must match the user's policy, and since the compiled configurations use communities to ensure only valid routes through the product graph are used, the resulting BGP configurations are Sound.

\begin{defn}
A distributed BGP configuration is \textit{Complete} with respect to a \sysname policy, if the distributed implementation always obtains a most preferred route between two nodes when the corresponding path exists in the network.
\end{defn}

The argument for completeness is as follows: Assume the most preferred path that exists in the network is between two nodes $X$ and $Y$.  This means there is a valid path in the product graph corresponding to this path, and which is available in the network. 
Assume we are unable to achieve this route in the network. To not achieve this path means that some router along the advertisement route from $Y$ to $X$ preferred to accept an advertisement from another peer instead. This implies that router that makes the ``wrong'' choice appears as a separate node in the product graph. However, from our failure safety check, we know that the other, more-preferred node must have a superset of the paths to accepting states as the less preferred node (from which it stole the route) for at least as good of a final preference. The argument then proceeds by induction on the path length - there are only a finite number of such stealings that can occur, each of which will ultimately still result in a route advertisement reaching $X$ along a most preferred path.

The combination of Soundness and Completeness ensures that the distributed implementation will always achieve the best routes possible, yet will never also use any unwanted routes.
